---
title: "HW1"
author: "Jieqi Tu"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

##  Question 1

#### (a)
$$\int^{\infty}_{0} x(1+x^{2})^{-2} dx$$\
Set $u = (1+x^2)$, then we can get: $\int^{\infty}_{0} x(1+x^{2})^{-2} dx = \frac{1}{2}\int^{\infty}_{1}u^{-2}du=\frac{1}{2}$\
In order to transform $\int^{\infty}_{0}$ to $\int^{1}_{0}$, set $y=\frac{1}{1+x}$.\
So $dx=-\frac{1}{y^2}dy$. Then we have $\int^{0}_{1}-\frac{1}{y^2}\frac{(1/y-1)}{(1+(1/y-1)^2)^{2}}dy$.
```{r question1 a}
# set seed
set.seed(1029)

# check theoretical value of the given integral using R:
integral_a = function(x) {
  x*(1+x^{2})^{-2}
}
integrate(integral_a, lower = 0, upper = Inf)$value
# simulate using uniform distribution
s = runif(100000)
transform = (1/s^2)*(1/s-1)/(1+(1/s-1)^2)^2
mean(transform)
```


#### (b)
$$\int^{\infty}_{-\infty} e^{-x^2}dx$$\
Because we already know the probability density function of Normal distribution: $f(x)=\frac{1}{\sigma \sqrt{2\pi}}e^{-\frac{1}{2}\frac{(x-\mu)^2}{\sigma^2}}$, we can let $\mu=1$, $\sigma=1/\sqrt{2}$.
Then according to the property of probability density function, we have: $\int^{\infty}_{-\infty} e^{x^2}dx = \sqrt{\pi}$\
To transform upper bound and lower bound, let $y = \frac{e^x}{1+e^x}$. Then we have $\int^{1}_{0} e^{\frac{logit^2(y)}{y(1-y)}}dy$

```{r question 1 b}
# set seed
set.seed(1029)

# check theoretical value of the given integral using R:
integral_b = function(x) {
  exp(-x^2)
}
integrate(integral_b, lower = -Inf, upper = Inf)$value
# simulate using uniform distribution
s = runif(100000)
transform = exp(-(log(s/(1-s)))^2)/(s*(1-s))
mean(transform)
```

#### (c)
$$\int^{4}_{2} ln{x}dx$$\
$\int^{4}_{2} lnxdx=xln{x}|_{2}^{4}-\int^{4}_{2} xdlnx=4ln4-2ln2-2\approx2.1588$. To transform the upper and lower bound, set $y=\frac{x-2}{2}$. Then we have$\int^{1}_{0} 2ln{(2y+2)}dy$.
```{r question 1 c}
# set seed
set.seed(1029)

# check theoretical value of the given integral using R:
integral_c = function(x) {
  log(x)
}
integrate(integral_c, lower = 2, upper = 4)$value
# simulate using uniform distribution
s = runif(1000000000)
transform = 2*log(2*s+2)
mean(transform)
```

#### (d)

$$\int^{1}_{0}\int^{1}_{0} e^{x+y} dxdy$$\
The exact value of this integral is $\int^{1}_{0}e^xdx\int^{1}_{0} e^{y}dy=(e-1)^2\approx2.952492$.
```{r question 1 d}
# set seed
set.seed(1029)

# simulate using uniform distribution
x = runif(100000)
y = runif(100000)
transform = exp(x+y)
mean(transform)
```

## Question 2
$Cov(U,\sqrt{1-U^2}=E(U^2\sqrt{1-U^2})-E(U^2)E(\sqrt{1-U^2})$.\
$E(U^2)=\int^{1}_{0}u^2du=u/3|^{1}_{0}=\frac{1}{3}$.\
Let $u=sin\theta, du/d\theta=cos\theta$. Then $E(U^2\sqrt{1-U^2})=\int^{\pi/2}_{0}sin^2\theta cos^2\theta d\theta=\int^{\pi/2}_{0}\frac{1}{4}sin^22\theta d\theta=\frac{1}{8}\int^{\pi/2}_{0}1-cos4\theta d\theta=\frac{\pi}{16}$\
$E(\sqrt{1-U^2})= \int_{0}^{1}\sqrt{1-u^2}du=\int_{0}^{\pi/2}cos\theta dsin\theta=\int_{0}^{\pi/2}cos^2\theta d\theta = \int_{0}^{\pi/2}\frac{1+cos2\theta}{2}d\theta=\\\int_{0}^{\pi/2}(\frac{1}{2}\theta+\frac{1}{4}sin2\theta)d\theta=\frac{\pi}{4}$\
$Cov(U^2,\sqrt{1-U^2})=\frac{\pi}{16}-\frac{1}{3}\times\frac{\pi}{4}\approx-0.06544985$
```{r question 2}
# set seed
set.seed(1029)

# simulate
u = runif(1000000)
y = u^2
z = sqrt(1 - y)
cov(y, z)
```

## Question 3
```{r question 3}
# set seed
set.seed(1029)

# simulate
sim_n = 10000
n_value = c()
for(i in 1:sim_n) {
  count = 0
  sum = 0
  while(sum <= 1) {
    u = runif(1)
    sum = sum + u
    count = count + 1
  }
  n_value[i] = count
}

mean(n_value)
```

## Question 4
```{r question 4}
# set seed
set.seed(1029)

# simulate
n_sim = 100000
n_value = c()
for (i in 1:n_sim) {
    count = 0
    prod = 1
  while(prod >=exp(-3)) {
    u = runif(1)
    prod = prod * u
    count = count + 1
  }
  n_value[i] = count
  
}
mean(n_value)
```

## Question 5
```{r question 5, warning=FALSE}
library(extraDistr)
set.seed(1029)
n_sim = 100000
n_list = numeric(n_sim) # to store all the values of the number of experiments
for (i in 1:n_sim) {
  d_list = c()
  statement = F
  n_value = 0
  while (statement == F) {
    sum = 0
    sum12 = sum(rdunif(2, 1, 6))
    n_value = n_value + 1
    d_list = c(d_list, sum12)
    for (j in 2:12) {
      # whether or not this outcome shows up in our experiments
      within = as.numeric(j %in% d_list) 
      sum = sum + within
    }
     # If one outcome is not present in the experiments, we will start a new experiment
    statement = (sum == 11)
  }
  n_list[i] = n_value
  }
round(mean(n_list))

```

## Question 6
#### (a)
Since $p_{j}=\frac{(j-1)!}{(j-r)!(r-1)!}p^r(1-p)^{j-r}$, $p_{j+1}=\frac{(j)!}{(j+1-r)!(r-1)!}p^r(1-p)^{j+1-r}$, we have $\frac{p_{j+1}}{p_{j}}=j(1-p)/(j+1-r)$

#### (b)
The algorithm to generate a negative binomial variable:

* Generate a random variable U, which follows uniform distribution. $U\sim Uniform(0, 1)$. In this case, $r$ means the number of success in a total number of $j$ trials. However, the last trial is defined to be successful.
* Set $c=1-p$, $j=r$, $pr=p^r$, and $F=pr$.
* If $U<F$, stop and report $j$.
* Then update: $pr=\frac{c*pr}{j+1-r}pr$, $F=F+pr$, $j=j+1$.
* Go to step 3 and repeat.

#### (c)
Theoretical value calculation:$E(X)=\frac{rp}{1-p}=\frac{5}{0.6}=12.5$, $Var(X)=\frac{r(1-p)}{p^2}=\frac{5*0.6}{0.16}=18.75$
```{r question 6 c}
# set seed
set.seed(1029)

# simulate
n_sim = 1000000
p = 0.4
r = 5
c = 1 - p
n_value = c()
for (i in 1:n_sim) {
  j = r
  pr = p^r
  u = runif(1, 0, 1)
  F_store = pr
  while (u>F_store) {
    pr = c*pr*j/(j+1-r)
    F_store = F_store + pr
    j = j + 1
  }
  n_value[i] = j
}

mean(n_value)
var(n_value)
```

## Question 7
Brute force to solve $E(|Z|)$:\
$E(|Z|)=2\int^{\infty}_{0}z\frac{1}{\sqrt{2\pi}}e^{-\frac{1}{2}z^2}dz=$. Let $u=e^{-\frac{1}{2}z^2}$, then we have $du/dz=-ze^{-\frac{1}{2}z^2}$. So $E(|Z|)=-\int^{0}_{1} \frac{2}{\sqrt{2\pi}}du=\frac{2}{\sqrt{2\pi}}\approx0.798$
```{r question 7}
set.seed(1029)

# create a large number of standard normally distributed variables
z = rnorm(10000000, 0, 1)
abs_z = abs(z)

# check the average
mean(abs_z)
```

## Question 8
$E(X)=\int^{1}_{0}x\frac{e^x}{e-1}dx=\frac{1}{e-1}e^x(x-1)|^{1}_{0}\approx0.581977$.\
$Var(X)=E(X^2)-(E(X))^2=\frac{1}{e-1}\int^{1}_{0}x^2e^xdx-(\frac{1}{e-1})^2=\frac{e-2}{e-1}-(\frac{1}{e-1})^2\approx0.079326$
Simulation algorithm:
Let $F(X)$ be the CDF for x, so $F(X)=\frac{1}{e-1}\int^{x}_{0}e^tdt=\frac{1}{e-1}(e^x-1)$.\
Let $U=F(X)$, then $U\sim Uniform(0,1)$. So we have $x=log[(e-1)u+1]$.
```{r question 8}
# set.seed
set.seed(1029)

# simulate
n_sim = 100000
x_value = c()
  
for(i in 1:n_sim) {
  # create the CDF for X
  u = runif(1, 0, 1)
  # express X using CDF
  x = log((exp(1)-1)*u+1)
  x_value[i] = x
}

mean(x_value)
var(x_value)
```

